Testing atlantisom: visualize weight at (st)age output. How shall we interplolate this for true ages?

### 2019-05-16 TestWeightAtStage.Rmd
improving wtage plots

wageplot <- ggplot(ss_length_census$muweight, aes(agecl)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_census$muweight$species))

wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
wageplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

How much does weight at age class vary over time?

Aggregate wt age stage over all of these time steps (first 22+ years):

```{r aggwtcomp, eval=FALSE}
#this isn't appropriate
wageplot

>>>>

wageplot <- ggplot(length_census$muweight, aes(agecl, atoutput)) +
  geom_point(aes(colour = time)) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits=c(1:10)) +
  xlab("age class") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste(scenario.name))

wageplot + facet_wrap(c("species"), scales="free_y")

@@

How much does weight at age class vary over time? Here are a couple of annual cycles:

```{r vis-wtageclass-test2}

wtageyr1 <- length_census$muweight %>%
  filter(time<5)

wageplot <- ggplot(wtageyr1, aes(agecl, atoutput)) +
  geom_line(aes(colour = factor(time))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits=c(1:10)) +
  xlab("age class") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " initial year"))

wageplot + facet_wrap(c("species"), scales="free_y")

```
```{r vis-wtageclass-test3}

wtageyrmid <- length_census$muweight %>%
  filter(between(time, 50,54))

wageplot <- ggplot(wtageyrmid, aes(agecl, atoutput)) +
  geom_line(aes(colour = factor(time))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits=c(1:10)) +
  xlab("age class") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " year 10"))

wageplot + facet_wrap(c("species"), scales="free_y")

```
```{r vis-wtageclass-test4}

wtageyr20 <- length_census$muweight %>%
  filter(between(time, 100,104))

wageplot <- ggplot(wtageyr20, aes(agecl, atoutput)) +
  geom_line(aes(colour = factor(time))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits=c(1:10)) +
  xlab("age class") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " year 20"))

wageplot + facet_wrap(c("species"), scales="free_y")

There are some interesting jumps between age classes. Most pronounced for herring, but those are real age classes!

Change in wt at age over time for age classes using an annual mid-year snapshot (survey) (first 22+ years of NOBA model run):

```{r aggwtcomp}

# from std survey code and model step info read in above
midptyr <- round(median(seq(1,stepperyr)))
annualmidyear <- seq(midptyr, noutsteps, stepperyr)

wtage_annsurv <- length_census$muweight %>%
  filter(time %in% annualmidyear)

wageplot <- ggplot(wtage_annsurv, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
